Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-12 rnni_convexity.tex
i think there is an error in lemma:mrca_move statement. fixed the error. hope the proof goes through

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage[misc]{ifsym}
\usepackage[foot]{amsaddr}
\usepackage[hidelinks]{hyperref}
\usepackage{csquotes}
%\usepackage[notref,notcite]{showkeys}
\usepackage[style=authoryear,ibidtracker=false,uniquename=false,giveninits=true,terseinits=true,maxbibnames=5,backend=biber]{biblatex}
\renewbibmacro{in:}{}
\addbibresource{rnni_convexity.bib}

@@

\begin{lemma}
Let $T = [C_1, \ldots, C_{k-1}, B_{k}, \ldots, B_{n-2}]$ and $R = [C_1, \ldots, C_{k-1}, C_k, \ldots, C_{n-2}]$ be two trees such that $C_k \neq B_k, \ldots, B_{n-2}$.
Then there exists exactly one $\rnni$ move on $T$ that results in a tree $T'$ such that $\mrca_{T'}(C_k) < \mrca_{T}(C_k)$.
\label{lemma:mrca_move}
\end{lemma}

>>>>

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[UKenglish]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{float}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{todonotes}
\usepackage{enumitem}
\usepackage[misc]{ifsym}
\usepackage[foot]{amsaddr}
\usepackage[hidelinks]{hyperref}
\usepackage{csquotes}
\usepackage[notref,notcite]{showkeys}
\usepackage[style=authoryear,ibidtracker=false,uniquename=false,giveninits=true,terseinits=true,maxbibnames=5,backend=biber]{biblatex}
\renewbibmacro{in:}{}
\addbibresource{rnni_convexity.bib}

@@

\begin{lemma}
Let $T = [C_1, \ldots, C_{k-1}, B_{k}, \ldots, B_{n-2}]$ and $R = [C_1, \ldots, C_{k-1}, C_k, \ldots, C_{n-2}]$ be two trees such that $C_k \neq B_k$.
Then there exists exactly one $\rnni$ move on $T$ that results in a tree $T'$ such that $\mrca_{T'}(C_k) < \mrca_{T}(C_k)$.
\label{lemma:mrca_move}
\end{lemma}
